Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 PandaEvolution.tex
Address Shantenu's comment

Titan's architecture, configuration and policies poses several challenges to
the integration with PanDA. The \jhanote{default?} deployment model of PanDA
Pilot is unfeasible on Titan: PanDA Pilot is required to contact the Job
Dispatcher of the PanDA Server to pull jobs to execute, but this is not
possible on Titan because worker nodes do not offer outbound network
connectivity. Further, Titan does not support PanDA's security model based on
certificates and virtual organizations, making PanDA's approach to
identity management also unfeasible. While DTNs offer wide area network data
transfer, an integration with ATLAS DDM is beyond the functional and
administrative scope of the current prototyping phase. Finally, the specific
characteristics of the execution environment, especially the absence of local
storage on the worker nodes and modules tailored to Compute Node Linux,
require re-engineering of ATLAS application frameworks.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_broker_architecture.pdf}
    \caption{PanDA Broker architecture as deployed on Titan. Numbers indicates
    the execution process of a detector simulation job, part of the production
    ATLAS MD workflow. \jhanote{minor error in figure: "ATLAS MC" not "MD"}}
\label{fig:panda_broker}
\end{figure}

>>>>

Titan's architecture, configuration and policies poses several challenges to the
integration with PanDA. The \jhanote{default?}\mtnote{Done.} default deployment
model of PanDA Pilot is unfeasible on Titan: PanDA Pilot is required to contact
the Job Dispatcher of the PanDA Server to pull jobs to execute, but this is not
possible on Titan because worker nodes do not offer outbound network
connectivity. Further, Titan does not support PanDA's security model based on
certificates and virtual organizations, making PanDA's approach to identity
management also unfeasible. While DTNs offer wide area network data transfer, an
integration with ATLAS DDM is beyond the functional and administrative scope of
the current prototyping phase. Finally, the specific characteristics of the
execution environment, especially the absence of local storage on the worker
nodes and modules tailored to Compute Node Linux, require re-engineering of
ATLAS application frameworks.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_broker_architecture.pdf}
    \caption{PanDA Broker architecture as deployed on Titan. Numbers indicates
    the execution process of a detector simulation job, part of the production
    ATLAS MD workflow. \jhanote{minor error in figure: "ATLAS MC" not "MD"}\mtnote{Fixed.}}
\label{fig:panda_broker}
\end{figure}
